Lattice Boltzmann study of mass transfer for complicated geometries

### 2012-01-26 Text/introduction.tex
Established the truth about mass transfer coefficient. Need one more simulation.

\section{Performing average approach}
One can calculate the average domain concentration over the time. According to the definitions of
the volumetric mass transfer coefficient one can obtain the following concentration depending on
time, i.e. streamwise coordinate:
\beqal
&\vol t \frac{\ububble}{\ugas+\uliq}=\ln\frac{C^*}{C^*-C(t)}\\
&\vol \frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble t} \ln \frac{C^*}{C^*-C(t)}\\
\feqal
Simulations for coefficient $\vol \frac{\ububble}{\ugas+\uliq}$ are shown in Fig.
\ref{fig:aver:conc:different:capillaries}.
\begin{figure}
\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca026.eps}
\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca054.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca05.eps}
\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca097.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca14.eps}\\
\caption{Volumetric mass transfer coefficient for different capillaries and scales. One can see the
excellent agreement. \label{fig:aver:conc:different:capillaries}}
\end{figure}
One of interesting correlations for the mass transfer volumetric coefficient was presented by
\citet{yue-mass}:
\beqal
&\vol=\frac{2}{d_h}\Bigl(\frac{D \ububble}{\lbubble+\lslug}\Bigr)^{0.5}
\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^0.3\\
&\vol \frac{\lunit}{\ugas+\uliq}=2\frac{\lunit}{d_h} \Bigl(\frac{D \varepsilon
}{(\ububble+\ugas)\lbubble+\lslug}\Bigr)^{0.5}
\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^0.3 \propto Pe^{-\frac{1}{2}}.
\feqal
\begin{figure}
\includegraphics[width=\textwidth]{Figures/volumetric_mass_peclet.eps}
\end{figure}

\section{Real calculations}
This section examines different cells for the capillary $Ca=0.097$. The coefficient is
non-dimensionalized in the following manner $\vol \frac{\lunit}{\ugas+\uliq}$. Therefore, we
examined the average concentrations in different units and for different scalings. Therefore the
average concentration between two different cells have to be of the following value:
\beqal
&C_1=C(x)=C^* \Bigl(1-e^{-\vol \frac{x}{\ugas+\uliq}}\Bigr)\\
&C_2=C(x+L)=C^* \Bigl(1-e^{-\vol \frac{x+L}{\ugas+\uliq}}\Bigr)\\
k_L\frac{L}{\ugas+\uliq}=\frac{C^*-C_1}{C^{*}-C_2}
\feqal
One can see that this number is different in comparison with the number used for periodic boundary
conditions. Thus, the domain transformation from time domain to the coordinate domain is not
straightforward and require other definitions. For example by definition we took $C_1$ and $C_2$ to
be average concentrations over different units. One can see Fig. \ref{fig:unit:8:scale:10} for
average coefficients and corresponding volumetric mass transfer coefficients.
\subsection{4 units}
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale10.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale10.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale15.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale15.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale20.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale20.eps}\\
\caption{Average concentrations and volumetric coefficients for $4$ units.
\label{fig:unit:4}}
\end{figure}

@@

@@

>>>>

\section{Performing average approach}
One can calculate the average domain concentration over the time. According to the definitions of
the volumetric mass transfer coefficient one can obtain the following concentration depending on
time, i.e. streamwise coordinate:
\beqal
&\vol t \frac{\ububble}{\ugas+\uliq}=\ln\frac{C^*}{C^*-C(t)}\\
&\vol \frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble t} \ln \frac{C^*}{C^*-C(t)}\\
\feqal
Simulations for coefficient $\vol \frac{\ububble}{\ugas+\uliq}$ are shown in Fig.
\ref{fig:aver:conc:different:capillaries}.
\begin{figure}
\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca026.eps}
\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca054.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca05.eps}
\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca097.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_conc_scale_ca14.eps}\\
\caption{Volumetric mass transfer coefficient for different capillaries and scales. One can see the
excellent agreement. \label{fig:aver:conc:different:capillaries}}
\end{figure}
One of interesting correlations for the mass transfer volumetric coefficient was presented by
\citet{yue-mass}:
\beqal
&\vol=\frac{2}{d_h}\Bigl(\frac{D \ububble}{\lbubble+\lslug}\Bigr)^{0.5}
\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^{0.3}\\
&\vol \frac{\lunit}{\ugas+\uliq}=2\frac{\lunit}{d_h} \Bigl(\frac{D 
}{\lunit (\ububble+\ugas)} \frac{\ububble}{\ugas+\uliq}\Bigr)^{0.5}
\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^{0.3} \propto Pe^{-\frac{1}{2}}\\
&\vol \frac{\lunit}{\ugas+\uliq}=2\frac{\lunit}{d_h} \Bigl(\frac{D 
}{\lunit (\ububble+\ugas)} \frac{\ububble}{\ugas+\uliq}\Bigr)^{0.5}
\Bigl(\frac{\lbubble}{\lbubble+\lslug}\Bigr)^{0.3} \propto Pe^{-\frac{1}{2}}
\feqal
\begin{figure}
\includegraphics[width=\textwidth]{Figures/volumetric_mass_peclet.eps}
\end{figure}

\section{Real calculations}
This section examines different cells for the capillary $Ca=0.097$. The coefficient is
non-dimensionalized in the following manner $\vol \frac{\lunit}{\ugas+\uliq}$. Therefore, we
examined the average concentrations in different units and for different scalings. Therefore the
average concentration between two different cells have to be of the following value:
\beqal
&C_1=C(x)=C^* \Bigl(1-e^{-\vol \frac{x}{\ugas+\uliq}}\Bigr)\\
&C_2=C(x+L)=C^* \Bigl(1-e^{-\vol \frac{x+L}{\ugas+\uliq}}\Bigr)\\
k_L\frac{L}{\ugas+\uliq}=\frac{C^*-C_1}{C^{*}-C_2}
\feqal
One can see that this number is different in comparison with the number used for periodic boundary
conditions. Thus, the domain transformation from time domain to the coordinate domain is not
straightforward and require other definitions. For example by definition we took $C_1$ and $C_2$ to
be average concentrations over different units. One can see Fig. \ref{fig:unit:8} for
average coefficients and corresponding volumetric mass transfer coefficients.
\subsection{4 units}
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale10.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale10.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale15.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale15.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units4scale20.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units4scale20.eps}\\
\caption{Average concentrations and volumetric coefficients for $4$ units.
\label{fig:unit:4}}
\end{figure}
The more interesting picture is actually moving window average which is calculated as:
\beq
\label{moving:average}
\vol\frac{\lunit}{\ugas+\uliq}=\frac{\lunit}{\ububble (t_2
-t_1)}\ln\Bigl(\frac{C^*-C_1}{C^*-C_2}\Bigr)
\feq
One can see those moving averages in Fig. \ref{window4}.
\begin{figure}[htb!]
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window4scale10.eps}\\
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window4scale15.eps}\\
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window4scale20.eps}\\
\caption{Moving averages defined in Eq. \ref{moving:average} for 4 units
\label{fig:moving:average:window4}}
\end{figure}

\subsection{6 units} 
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/aver_units6scale10.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units6scale10.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units6scale15.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units6scale15.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/aver_units6scale20.eps}\hfill
\includegraphics[width=0.5\textwidth]{Figures/coeff_units6scale20.eps}\\
\caption{Average concentrations and volumetric coefficients for $8$ units.
\label{fig:unit:10}}
\end{figure}

Another moving concentrations window is presented in Fig. \ref{fig:moving:average:window6}.
\begin{figure}[htb!]
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window6scale10.eps}\\
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window6scale15.eps}\\
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window6scale20.eps}\\
\caption{Moving averages defined in Eq. \ref{moving:average} for $8$ units.
\label{fig:moving:average:window6}}
\end{figure}

@@

Another moving concentrations window is presented in Fig. \ref{fig:moving:average:window8}.
\begin{figure}[htb!]
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window8scale10.eps}\\
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window8scale15.eps}\\
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window8scale20.eps}\\
\caption{Moving averages defined in Eq. \ref{moving:average} for $8$ units.
\label{fig:moving:average:window8}}
\end{figure}

@@

Another moving concentrations window is presented in Fig. \ref{fig:moving:average:window10}.
\begin{figure}[htb!]
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window10scale10.eps}\\
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window10scale15.eps}\\
\includegraphics[width=0.7\textwidth]{Figures/aver_moving_window10scale20.eps}\\
\caption{Moving averages defined in Eq. \ref{moving:average} for $8$ units.
\label{fig:moving:average:window10}}
\end{figure}

\section{Open boundary conditions}
\begin{figure}
\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0097.eps}
\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0097.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/jos_aver_conc_scale_ca0254.eps}
\includegraphics[width=0.5\textwidth]{Figures/jos_aver_moving_window_ca0254.eps}\\
\caption{Open boundary conditions. \label{fig:open:boundary:jos}}
\end{figure}

\section{Symmetric boundary conditions}
\begin{figure}
\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0097.eps}
\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0097.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/sym_aver_conc_scale_ca0254.eps}
\includegraphics[width=0.5\textwidth]{Figures/sym_aver_moving_window_ca0254.eps}\\
\caption{Symmetric boundary conditions. \label{fig:open:boundary:sym}}
\end{figure}
